Dissertation Proposal

### 2023-11-05 proposal.tex
save

[FILL]

@@

I would like to evaluate the effectiveness from two perspectives:
\begin{itemize}
  \item How effective is the tutor at stopping students from holding
        misconceptions?
  \item How close are students' final conception to the true
        conception?
\end{itemize}

@@

Given this observation, I plan to set up the tutor such that
\begin{itemize}
  \item Every wrong answer corresponds to up to one misconception. In
        this case, I say the wrong answer \emph{represents} the
        misconception.
  \item Every misconception is represented by some questions.
  \item In each tutorial, a misconception is either not represented by
        any interpreting tasks or represented by exactly two tasks.
  \item Within each tutorial, the order of interpreting tasks is
        randomized.
\end{itemize}

For each tutorail and each misconception appear in the tutorial, I
compare student performance on the \emph{first} question that involve
the misconceptions with performance on the \emph{second} question. If
the difference is clear (i.e., ``statistically significant''), I
deduce that the tutor is effective at correcting the misconception.

>>>>

[FILL] Use a random default syntax per task? Log syntax switch.

@@

I would like to evaluate the effectiveness from two perspectives:
\begin{itemize}
  \item How effective is the tutor at stopping students from holding
        misconceptions?
\end{itemize}

@@

Given this observation, I plan to set up the tutor such that
\begin{itemize}
  \item Every wrong answer corresponds to up to one misconception. In
        this case, I say the wrong answer \emph{represents} the
        misconception.
  \item Every misconception is represented by some questions.
  \item In each tutorial, a misconception is either not represented by
        any interpreting tasks or represented by at least two tasks.
  \item Within each tutorial, the order of interpreting tasks is
        randomized.
\end{itemize}
For each tutorial and each misconception, I plan to do a model
comparison (with the standard AIC and BIC criteria) on the following
models/theories:
\begin{description}
  \item[TaskSpecific] Some students are more likely to choose the
  representing wrong answers in certain tasks.
  \item[PositionSpecific] Students are more likely to choose the
  representing wrong answer in a task if the task appears earlier (or
  later) in the tutorial.
\end{description}

If the \textbf{TaskSpecific} model best explains the data, I deduce
that some programs are more confusing and that we need further
investigation into the relationship between the tasks and misconceptions.

If the \textbf{PositionSpecific} model best explains \emph{and} students
perform better in later tasks, I deduce that the tutor seeems to be
correcting misconceptions. If studnets perform worse in later taks, the
tutor is potentially doing harm.

To know students well, I would like to have as many tasks per
misconception as possible. But in practice, the number of tasks is
subject to the following limitations:
\begin{enumerate}
  \item I don't want the length of any tutorial to exceed 30 minutes.
  Because the tutor is now asking for student explanation on choice,
  students are likely to spend more time on each task then before.
  \item Programs shouldn't be too long. Some misconceptions are really
  similar and as a consequence have only a small number of short
  programs to tell them apart.
\end{enumerate}

The current tutor is not in the final shape yet. In particular, many
of the wrong answers correspond to more than one misconceptions; some
misconceptions are represented by only one question; the order of
interpreting tasks are not randomized. I plan to tackles the first two
differences by adding and removing programs. Adding randomization
requires me to carefully check the dependencies between current
explanations and goal sentences and resolve those dependencies if any.
